---
title: "Final Project: HIP Analysis"
author: "Ariunjargal Khaltarkhuu"
date: today
format: pdf
editor: source
---
# Install and Load Packages

```{r}
#install.packages(c(
  "tidyverse",
  "readtext",
  "tidytext",
  "quanteda",
  "quanteda.textstats",
  "quanteda.textplots",
  "topicmodels",
  "stm",
  "janitor",
  "stringr",
  "lubridate",
  "textstem",
  "widyr",
  "tidylo"
))
```

```{r}
library(tidyverse)
library(readtext)
library(tidytext)
library(quanteda)
library(quanteda.textstats)
library(quanteda.textplots)
library(topicmodels)
library(stm)
library(janitor)
library(stringr)
library(lubridate)
library(textstem)
library(widyr)
library(tidylo)
```

# Import and merge all text, metadata
```{r}
journals <- readtext("data_clean_archival/journals/*.txt")
interviews <- readtext("data_clean_archival/interviews/*.txt")
```

```{r}
all_text <- bind_rows(journals, interviews)
```

```{r}
all_text <- all_text %>%
  rename(file_name = doc_id,
         text_original = text)
```

```{r}
library(readr)
library(janitor)

meta <- read_csv("metadata/document_metadata.csv") %>%
  clean_names()
```

```{r}
summary(meta)
```

```{r}
glimpse(meta)
```

```{r}
table(meta$participant_type, useNA = "ifany")
table(meta$week_number, useNA = "ifany")
table(meta$work_mode, useNA = "ifany")
```

```{r}
library(dplyr)
library(stringr)
library(readr)

meta <- read_csv("metadata/document_metadata.csv")

meta <- meta %>%
  mutate(
    organization_name = str_trim(organization_name),
    organization_name = case_when(
      organization_name == "Engineers Without Border" ~ "Engineers Without Borders",
      organization_name == "Save The Children" ~ "Save the Children",
      organization_name == "GWU" ~ "George Washington University",
      TRUE ~ organization_name
    )
  )

sort(unique(meta$organization_name))

write_csv(meta, "metadata/document_metadata.csv")
```

```{r}
meta %>%
  count(organization_name, sort = TRUE)
```

```{r}
all_text <- bind_rows(journals, interviews) %>%
  rename(file_name = doc_id,
         text_original = text)

corpus_df <- all_text %>%
  left_join(meta, by = "file_name")
```

```{r}
glimpse(corpus_df)
sum(is.na(corpus_df$doc_id.y))
```

```{r}
library(dplyr)

all_text <- bind_rows(journals, interviews) %>%
  rename(
    file_name = doc_id,
    text_original = text
  )

corpus_df <- all_text %>%
  left_join(meta, by = "file_name")
```

```{r}
glimpse(corpus_df)

sum(is.na(corpus_df$doc_id.y))
sum(is.na(corpus_df$participant_type))
```

```{r}
names(corpus_df)
```

```{r}
corpus_df %>%
  filter(is.na(participant_type)) %>%
  select(file_name)
```

```{r}
all_text %>%
  anti_join(meta, by = "file_name") %>%
  select(file_name)
```

```{r}
meta %>%
  anti_join(all_text, by = "file_name") %>%
  select(file_name)
```

```{r}
corpus_df <- all_text %>%
  left_join(meta, by = "file_name")
```

```{r}
meta <- read_csv("metadata/document_metadata.csv") %>%
  clean_names()

meta <- meta %>%
  mutate(
    file_name = if_else(
      file_name == "supervisor_13_finalinterview.txt",
      "supervisor_13-finalinterview.txt",
      file_name
    )
  )

all_text <- bind_rows(journals, interviews) %>%
  rename(
    file_name = doc_id,
    text_original = text
  )

corpus_df <- all_text %>%
  left_join(meta, by = "file_name")

sum(is.na(corpus_df$participant_type))
```

# Create method specific corpus
```{r}
library(stringr)
library(dplyr)

corpus_df <- corpus_df %>%
  as_tibble() %>%
  mutate(
    text_ner = str_squish(text_original),

    text_tf = text_original %>%
      str_replace_all("\\[.*?\\]", " ") %>%
      str_to_lower() %>%
      str_replace_all("[^[:alnum:]\\s]", " ") %>%
      str_squish(),

    text_lda = text_original %>%
      str_replace_all("\\[.*?\\]", " ") %>%
      str_to_lower() %>%
      str_replace_all("[^[:alnum:]\\s]", " ") %>%
      str_squish()
  )
```
```{r}
names(corpus_df)
```

```{r}
corpus_df <- corpus_df %>%
  mutate(word_count = str_count(text_original, "\\S+"))

corpus_df %>% count(participant_type)
corpus_df %>% count(early_late)
summary(corpus_df$word_count)
```

# Tokenization for TF/TF-IDF/N-grams
```{r}
data(stop_words)

tokens <- corpus_df %>%
  select(doc_id, participant_type, early_late, cohort_year, organization_name, work_mode, text_tf) %>%
  unnest_tokens(word, text_tf)

tokens_clean <- tokens %>%
  anti_join(stop_words, by = "word")
```

```{r}
tokens_clean %>% count(word, sort = TRUE)
```

## Inductive- TF stage
```{r}
library(tidyverse)
library(tidytext)
library(stringr)
library(forcats)
```

```{r}
names(corpus_df)
```
```{r}
data(stop_words)

tokens <- corpus_df %>%
  select(
    doc_id,
    participant_type,
    participant_id,
    week_number,
    timepoint,
    early_late,
    cohort_year,
    organization_name,
    work_mode,
    text_tf
  ) %>%
  unnest_tokens(word, text_tf)
```
```{r}
glimpse(tokens)
```
```{r}
tokens_nostop <- tokens %>%
  anti_join(stop_words, by = "word")
```

```{r}
generic_project_words <- tibble(
  word = c(
    "intern", "interns", "internship", "student", "students", "bit",
    "project", "projects", "work", "working", "worked", "guys",
    "organization", "team", "program", "week", "weeks", "yeah",
    "really", "also", "would", "could", "one", "like", "just", "lot", "don", "day", "didn", "ve"
  )
)

tokens_clean <- tokens_nostop %>%
  anti_join(generic_project_words, by = "word")
```

```{r}
tokens_clean %>%
  count(word, sort = TRUE)
```

# Top words in student journals
```{r}
tf_students <- tokens_clean %>%
  filter(participant_type == "student") %>%
  count(word, sort = TRUE)

tf_students %>% slice_head(n = 25)
```

# Top words in supervisor interviews
```{r}
tf_supervisors <- tokens_clean %>%
  filter(participant_type == "supervisor") %>%
  count(word, sort = TRUE)

tf_supervisors %>% slice_head(n = 25)
```

# Visualize top words by participant type
```{r}
tf_top10_plot <- tf_by_type %>%
  group_by(participant_type) %>%
  slice_max(n, n = 10, with_ties = FALSE) %>%
  ungroup() %>%
  mutate(word = tidytext::reorder_within(word, n, participant_type)) %>%
  ggplot(aes(x = word, y = n)) +
  geom_col() +
  coord_flip() +
  tidytext::scale_x_reordered() +
  facet_wrap(~ participant_type, scales = "free_y") +
  labs(
    title = "Top 10 Words by Participant Type",
    x = NULL,
    y = "Term Frequency"
  )

tf_top10_plot
```

```{r}
ggsave(
  "outputs/figures/top10_words_by_participant_type.png",
  tf_top10_plot,
  width = 8,
  height = 6
)
```

# TF within positive, challenge, and skill-related contexts
```{r}
positive_seed <- c(
  "support", "helpful", "help", "great", "good", "positive",
  "confident", "confidence", "growth", "learning", "learned",
  "mentorship", "mentor", "professional", "success", "successful",
  "valuable", "meaningful", "prepared", "strong", "excited"
)
```

```{r}
challenge_seed <- c(
  "challenge", "challenges", "difficult", "difficulty", "hard",
  "unclear", "confusing", "stress", "stressed", "workload",
  "communication", "issue", "issues", "problem", "problems",
  "uncertainty", "logistics", "remote", "time", "busy"
)
```

```{r}
skill_seed <- c(
  "communication", "leadership", "analysis", "analytical",
  "research", "writing", "management", "teamwork", "collaboration",
  "problem", "technical", "data", "presentation", "organization"
)
```

# Create context-level subsets

```{r}
positive_docs <- tokens_clean %>%
  filter(word %in% positive_seed) %>%
  distinct(doc_id)

tokens_positive <- tokens_clean %>%
  semi_join(positive_docs, by = "doc_id")
```

```{r}
challenge_docs <- tokens_clean %>%
  filter(word %in% challenge_seed) %>%
  distinct(doc_id)

tokens_challenge <- tokens_clean %>%
  semi_join(challenge_docs, by = "doc_id")
```

```{r}
skill_docs <- tokens_clean %>%
  filter(word %in% skill_seed) %>%
  distinct(doc_id)

tokens_skill <- tokens_clean %>%
  semi_join(skill_docs, by = "doc_id")
```

# TF for positive/strength-related terms
```{r}
tf_positive_students <- tokens_positive %>%
  filter(participant_type == "student") %>%
  count(word, sort = TRUE)

tf_positive_students %>% slice_head(n = 20)
```

```{r}
tf_positive_supervisors <- tokens_positive %>%
  filter(participant_type == "supervisor") %>%
  count(word, sort = TRUE)

tf_positive_supervisors %>% slice_head(n = 20)
```

```{r}
bind_rows(
  tf_positive_students %>% mutate(group = "student"),
  tf_positive_supervisors %>% mutate(group = "supervisor")
) %>%
  group_by(group) %>%
  slice_max(n, n = 10) %>%
  ungroup() %>%
  mutate(word = reorder_within(word, n, group)) %>%
  ggplot(aes(x = word, y = n)) +
  geom_col() +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ group, scales = "free_y") +
  labs(
    title = "Top Words in Positive/Strength-Related Contexts",
    x = NULL,
    y = "Term Frequency"
  )
```

```{r}
positive_plot <- bind_rows(
  tf_positive_students %>% mutate(group = "student"),
  tf_positive_supervisors %>% mutate(group = "supervisor")
) %>%
  group_by(group) %>%
  slice_max(n, n = 10, with_ties = FALSE) %>%
  ungroup() %>%
  mutate(word = reorder_within(word, n, group)) %>%
  ggplot(aes(x = word, y = n)) +
  geom_col() +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ group, scales = "free_y") +
  labs(
    title = "Top Words in Positive/Strength-Related Contexts",
    x = NULL,
    y = "Term Frequency"
  )

ggsave(
  filename = "outputs/figures/top_words_positive_strength_contexts.png",
  plot = positive_plot,
  width = 8,
  height = 6,
  dpi = 300
)
```

# TF for challenge-related terms
```{r}
tf_challenge_by_type <- tokens_clean %>%
  filter(word %in% challenge_seed) %>%
  count(participant_type, word, sort = TRUE)

tf_challenge_top10 <- tf_challenge_by_type %>%
  group_by(participant_type) %>%
  slice_max(n, n = 10, with_ties = FALSE) %>%
  ungroup()

tf_challenge_top10
```

```{r}
challenge_plot <- tf_challenge_top10 %>%
  mutate(word = reorder_within(word, n, participant_type)) %>%
  ggplot(aes(x = word, y = n)) +
  geom_col() +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ participant_type, scales = "free_y") +
  labs(
    title = "Top 10 Challenge-Related Words by Participant Type",
    x = NULL,
    y = "Term Frequency"
  )

challenge_plot
```

```{r}
ggsave(
  filename = "outputs/figures/top10_challenge_words_by_participant_type.png",
  plot = challenge_plot,
  width = 8,
  height = 6,
  dpi = 300
)
```

```{r}
write_csv(
  tf_challenge_top10,
  "outputs/tables/top10_challenge_words_by_participant_type.csv"
)
```

# TF by subgroup- top words by early vs late among students
```{r}
tf_student_earlylate <- tokens_clean %>%
  filter(participant_type == "student") %>%
  count(early_late, word, sort = TRUE)

tf_student_earlylate %>%
  group_by(early_late) %>%
  slice_max(n, n = 15) %>%
  ungroup()
```

```{r}
tf_student_earlylate %>%
  group_by(early_late) %>%
  slice_max(n, n = 10) %>%
  ungroup() %>%
  mutate(word = reorder_within(word, n, early_late)) %>%
  ggplot(aes(x = word, y = n)) +
  geom_col() +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ early_late, scales = "free_y") +
  labs(
    title = "Top Words in Student Journals: Early vs Late",
    x = NULL,
    y = "Term Frequency"
  )
```

```{r}
tf_by_workmode <- tokens_clean %>%
  count(work_mode, word, sort = TRUE)

tf_by_workmode %>%
  group_by(work_mode) %>%
  slice_max(n, n = 15) %>%
  ungroup()
```

```{r}
tf_by_workmode <- tokens_clean %>%
  filter(!is.na(work_mode), work_mode != "NA") %>%
  count(work_mode, word, sort = TRUE)

workmode_plot <- tf_by_workmode %>%
  group_by(work_mode) %>%
  slice_max(n, n = 10, with_ties = FALSE) %>%
  ungroup() %>%
  mutate(word = reorder_within(word, n, work_mode)) %>%
  ggplot(aes(x = word, y = n)) +
  geom_col() +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ work_mode, scales = "free_y") +
  labs(
    title = "Top 10 Words by Work Mode",
    x = NULL,
    y = "Term Frequency"
  )

workmode_plot
```

```{r}
ggsave(
  filename = "outputs/figures/top10_words_by_work_mode.png",
  plot = workmode_plot,
  width = 8,
  height = 6,
  dpi = 300
)
```

## Inductive-TF-IDF stage

```{r}
library(tidyverse)
library(tidytext)
library(stringr)
library(forcats)

data(stop_words)

tokens <- corpus_df %>%
  select(
    doc_id,
    participant_type,
    participant_id,
    week_number,
    timepoint,
    early_late,
    cohort_year,
    organization_name,
    work_mode,
    text_tf
  ) %>%
  unnest_tokens(word, text_tf)

generic_project_words <- tibble(
  word = c(
    "intern", "interns", "internship", "internships", "set", "feel",
    "student", "students", "supervisor", "supervisors", "couple", "dhis2",
    "program", "programs", "project", "projects", "including", "wasn",
    "organization", "team", "work", "worked", "working", "00",
    "week", "weeks", "summer", "bit", "guys", "yeah", "so", "ll", "send",
    "gw", "hipp", "really", "also", "would", "could", "one", "like", "just", "lot", "don", "day", "didn", "ve", "pretty", "much", "thing", "things", "know", "got", "get", "getting", "people", "time", "times", "folks", "jasmine"
  )
)

tokens_clean <- tokens %>%
  anti_join(stop_words, by = "word") %>%
  anti_join(generic_project_words, by = "word")
```

# Compute by participant type

```{r}
tfidf_by_type <- tokens_clean %>%
  count(participant_type, word, sort = TRUE) %>%
  bind_tf_idf(word, participant_type, n) %>%
  arrange(desc(tf_idf))
```

```{r}
tfidf_top10_by_type <- tfidf_by_type %>%
  group_by(participant_type) %>%
  slice_max(tf_idf, n = 10, with_ties = FALSE) %>%
  ungroup()

tfidf_top10_by_type
```

```{r}
tfidf_type_plot <- tfidf_top10_by_type %>%
  mutate(word = reorder_within(word, tf_idf, participant_type)) %>%
  ggplot(aes(x = word, y = tf_idf)) +
  geom_col() +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ participant_type, scales = "free_y") +
  labs(
    title = "Top 10 Distinctive Words by Participant Type (TF-IDF)",
    x = NULL,
    y = "TF-IDF"
  )

tfidf_type_plot
```

```{r}
ggsave(
  filename = "outputs/figures/top10_tfidf_by_participant_type.png",
  plot = tfidf_type_plot,
  width = 8,
  height = 6,
  dpi = 300
)
```

```{r}
write_csv(
  tfidf_top10_by_type,
  "outputs/tables/top10_tfidf_by_participant_type.csv"
)
```

# Compute TF-IDF by early vs late journals

```{r}
tokens_students <- tokens_clean %>%
  filter(participant_type == "student")
```

```{r}
tfidf_earlylate <- tokens_students %>%
  count(early_late, word, sort = TRUE) %>%
  bind_tf_idf(word, early_late, n) %>%
  arrange(desc(tf_idf))
```

```{r}
tfidf_top10_earlylate <- tfidf_earlylate %>%
  group_by(early_late) %>%
  slice_max(tf_idf, n = 10, with_ties = FALSE) %>%
  ungroup()

tfidf_top10_earlylate
```

```{r}
tfidf_earlylate_plot <- tfidf_top10_earlylate %>%
  mutate(word = reorder_within(word, tf_idf, early_late)) %>%
  ggplot(aes(x = word, y = tf_idf)) +
  geom_col() +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ early_late, scales = "free_y") +
  labs(
    title = "Top 10 Distinctive Words in Early vs Late Student Reflections",
    x = NULL,
    y = "TF-IDF"
  )

tfidf_earlylate_plot
```

```{r}
ggsave(
  filename = "outputs/figures/top10_tfidf_early_vs_late.png",
  plot = tfidf_earlylate_plot,
  width = 8,
  height = 6,
  dpi = 300
)

write_csv(
  tfidf_top10_earlylate,
  "outputs/tables/top10_tfidf_early_vs_late.csv"
)
```

# Compute TF-IDF by work mode (wordcloud)
```{r}
# install.packages("ggwordcloud")
```

```{r}
library(ggwordcloud)
```

```{r}
tokens_workmode <- tokens_clean %>%
  filter(!is.na(work_mode), work_mode != "NA")

tfidf_workmode <- tokens_workmode %>%
  count(work_mode, word, sort = TRUE) %>%
  bind_tf_idf(word, work_mode, n) %>%
  arrange(desc(tf_idf))

tfidf_top10_workmode <- tfidf_workmode %>%
  group_by(work_mode) %>%
  slice_max(tf_idf, n = 20, with_ties = FALSE) %>%
  ungroup()

tfidf_top10_workmode
```

```{r}
tfidf_workmode_wordcloud <- tfidf_top10_workmode %>%
  ggplot(aes(label = word, size = tf_idf)) +
  geom_text_wordcloud_area() +
  facet_wrap(~ work_mode, scales = "free") +
  scale_size_area(max_size = 18) +
  labs(
    title = "Top 20 Distinctive Words by Work Mode (TF-IDF Word Cloud)"
  ) +
  theme_minimal()

tfidf_workmode_wordcloud
```

```{r}
ggsave(
  filename = "outputs/figures/top20_tfidf_wordcloud_by_work_mode.png",
  plot = tfidf_workmode_wordcloud,
  width = 10,
  height = 6,
  dpi = 300
)
```

```{r}
write_csv(
  tfidf_top10_workmode,
  "outputs/tables/top20_tfidf_by_work_mode.csv"
)
```

# RQ1: TF-IDF for strength-related terms
```{r}
positive_seed <- c(
  "support", "helpful", "help", "great", "good", "positive",
  "confident", "confidence", "growth", "learning", "learned",
  "mentorship", "mentor", "professional", "success", "successful",
  "valuable", "meaningful", "prepared", "strong", "excited"
)
```

```{r}
tfidf_strength_by_type <- tokens_clean %>%
  filter(word %in% positive_seed) %>%
  count(participant_type, word, sort = TRUE) %>%
  bind_tf_idf(word, participant_type, n) %>%
  arrange(desc(tf_idf))
```

```{r}
tfidf_strength_top10 <- tfidf_strength_by_type %>%
  group_by(participant_type) %>%
  slice_max(tf_idf, n = 10, with_ties = FALSE) %>%
  ungroup()

tfidf_strength_top10
```

```{r}
tfidf_strength_plot <- tfidf_strength_top10 %>%
  mutate(word = reorder_within(word, tf_idf, participant_type)) %>%
  ggplot(aes(x = word, y = tf_idf)) +
  geom_col() +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ participant_type, scales = "free_y") +
  labs(
    title = "Top 10 Distinctive Strength-Related Words by Participant Type",
    x = NULL,
    y = "TF-IDF"
  )

tfidf_strength_plot
```

```{r}
ggsave(
  filename = "outputs/figures/top10_tfidf_strength_by_participant_type.png",
  plot = tfidf_strength_plot,
  width = 8,
  height = 6,
  dpi = 300
)

write_csv(
  tfidf_strength_top10,
  "outputs/tables/top10_tfidf_strength_by_participant_type.csv"
)
```

```{r}
tfidf_strength_top10 %>%
  mutate(word = reorder_within(word, tf_idf, participant_type)) %>%
  ggplot(aes(x = word, y = tf_idf)) +
  geom_segment(aes(xend = word, y = 0, yend = tf_idf)) +
  geom_point(size = 3) +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ participant_type, scales = "free_y") +
  labs(
    title = "Distinctive Strength-Related Terms by Participant Type",
    x = NULL,
    y = "TF-IDF"
  )
```

```{r}
strength_lollipop_plot <- tfidf_strength_top10 %>%
  mutate(word = reorder_within(word, tf_idf, participant_type)) %>%
  ggplot(aes(x = word, y = tf_idf)) +
  geom_segment(aes(xend = word, y = 0, yend = tf_idf)) +
  geom_point(size = 3) +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ participant_type, scales = "free_y") +
  labs(
    title = "Distinctive Strength-Related Terms by Participant Type",
    x = NULL,
    y = "TF-IDF"
  )

strength_lollipop_plot

ggsave(
  filename = "outputs/figures/distinctive_strength_terms_lollipop.png",
  plot = strength_lollipop_plot,
  width = 8,
  height = 6,
  dpi = 300
)
```

```{r}
tfidf_strength_top10 %>%
  ggplot(aes(x = participant_type, y = word, fill = tf_idf)) +
  geom_tile() +
  labs(
    title = "Strength-Related TF-IDF by Participant Type",
    x = NULL,
    y = NULL,
    fill = "TF-IDF"
  )
```

```{r}
strength_heatmap <- tfidf_strength_top10 %>%
  ggplot(aes(x = participant_type, y = word, fill = tf_idf)) +
  geom_tile(color = "white") +
  labs(
    title = "Strength-Related TF-IDF by Participant Type",
    x = NULL,
    y = NULL,
    fill = "TF-IDF"
  )

strength_heatmap
```

```{r}
ggsave(
  filename = "outputs/figures/strength_tfidf_heatmap_by_participant_type.png",
  plot = strength_heatmap,
  width = 7,
  height = 6,
  dpi = 300
)
```

# RQ2: TF-IDF for challenge-related terms

```{r}
challenge_seed <- c(
  "challenge", "challenges", "difficult", "difficulty", "hard",
  "unclear", "confusing", "stress", "stressed", "workload",
  "communication", "issue", "issues", "problem", "problems",
  "uncertainty", "logistics", "remote", "time", "busy"
)
```

```{r}
tfidf_challenge_by_type <- tokens_clean %>%
  filter(word %in% challenge_seed) %>%
  count(participant_type, word, sort = TRUE) %>%
  bind_tf_idf(word, participant_type, n) %>%
  arrange(desc(tf_idf))
```

```{r}
tfidf_challenge_top10 <- tfidf_challenge_by_type %>%
  group_by(participant_type) %>%
  slice_max(tf_idf, n = 10, with_ties = FALSE) %>%
  ungroup()

tfidf_challenge_top10
```

```{r}
tfidf_challenge_plot <- tfidf_challenge_top10 %>%
  mutate(word = reorder_within(word, tf_idf, participant_type)) %>%
  ggplot(aes(x = word, y = tf_idf)) +
  geom_col() +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ participant_type, scales = "free_y") +
  labs(
    title = "Top 10 Distinctive Challenge-Related Words by Participant Type",
    x = NULL,
    y = "TF-IDF"
  )

tfidf_challenge_plot
```

```{r}
ggsave(
  filename = "outputs/figures/top10_tfidf_challenge_by_participant_type.png",
  plot = tfidf_challenge_plot,
  width = 8,
  height = 6,
  dpi = 300
)

write_csv(
  tfidf_challenge_top10,
  "outputs/tables/top10_tfidf_challenge_by_participant_type.csv"
)
```

```{r}
challenge_compare <- tfidf_challenge_by_type %>%
  filter(word %in% c("uncertainty", "stress", "confusing", "hard", "busy", "remote")) %>%
  select(participant_type, word, tf_idf)

ggplot(challenge_compare, aes(x = tf_idf, y = word, color = participant_type)) +
  geom_point(size = 3, position = position_dodge(width = 0.5)) +
  labs(
    title = "Challenge Language by Participant Type",
    x = "TF-IDF",
    y = NULL
  )
```

```{r}
challenge_compare <- tfidf_challenge_by_type %>%
  filter(word %in% c("uncertainty", "stress", "confusing", "hard", "busy", "remote")) %>%
  select(participant_type, word, tf_idf)

challenge_compare_plot <- ggplot(
  challenge_compare,
  aes(x = tf_idf, y = word, color = participant_type)
) +
  geom_point(size = 3, position = position_dodge(width = 0.5)) +
  labs(
    title = "Challenge Language by Participant Type",
    x = "TF-IDF",
    y = NULL
  )

challenge_compare_plot

ggsave(
  filename = "outputs/figures/challenge_language_by_participant_type.png",
  plot = challenge_compare_plot,
  width = 8,
  height = 6,
  dpi = 300
)
```

# 10. RQ3: skill-related language
```{r}
skill_seed <- c(
  "project", "management", "data", "analysis", "communication",
  "skills", "teamwork", "critical", "thinking", "report", "writing",
  "leadership", "research", "presentation", "collaboration"
)
```

```{r}
tfidf_skill_students <- tokens_clean %>%
  filter(participant_type == "student", word %in% skill_seed) %>%
  count(early_late, word, sort = TRUE) %>%
  bind_tf_idf(word, early_late, n) %>%
  arrange(desc(tf_idf))
```

```{r}
tfidf_skill_top10 <- tfidf_skill_students %>%
  group_by(early_late) %>%
  slice_max(tf_idf, n = 10, with_ties = FALSE) %>%
  ungroup()

tfidf_skill_top10
```

```{r}
tfidf_skill_plot <- tfidf_skill_top10 %>%
  mutate(word = reorder_within(word, tf_idf, early_late)) %>%
  ggplot(aes(x = word, y = tf_idf)) +
  geom_col() +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ early_late, scales = "free_y") +
  labs(
    title = "Top 10 Distinctive Skill-Related Words in Early vs Late Student Journals",
    x = NULL,
    y = "TF-IDF"
  )

tfidf_skill_plot
```

```{r}
ggsave(
  filename = "outputs/figures/top10_tfidf_skill_early_vs_late.png",
  plot = tfidf_skill_plot,
  width = 8,
  height = 6,
  dpi = 300
)

write_csv(
  tfidf_skill_top10,
  "outputs/tables/top10_tfidf_skill_early_vs_late.csv"
)
```

# RQ4: TF-IDF by subgroup
```{r}
tfidf_by_org <- tokens_clean %>%
  count(organization_name, word, sort = TRUE) %>%
  bind_tf_idf(word, organization_name, n) %>%
  arrange(desc(tf_idf))

tfidf_top10_by_org <- tfidf_by_org %>%
  group_by(organization_name) %>%
  slice_max(tf_idf, n = 10, with_ties = FALSE) %>%
  ungroup()
```

```{r}
tfidf_org_plot <- tfidf_top10_by_org %>%
  mutate(word = reorder_within(word, tf_idf, organization_name)) %>%
  ggplot(aes(x = word, y = tf_idf)) +
  geom_col() +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ organization_name, scales = "free_y") +
  labs(
    title = "Top 10 Distinctive Words by Organization",
    x = NULL,
    y = "TF-IDF"
  )

tfidf_org_plot
```

```{r}
ggsave(
  filename = "outputs/figures/top10_tfidf_by_organization.png",
  plot = tfidf_org_plot,
  width = 10,
  height = 8,
  dpi = 300
)

write_csv(
  tfidf_top10_by_org,
  "outputs/tables/top10_tfidf_by_organization.csv"
)
```

```{r}
tfidf_by_type <- tokens_clean %>%
  count(participant_type, word, sort = TRUE) %>%
  bind_tf_idf(word, participant_type, n) %>%
  arrange(desc(tf_idf))

tfidf_top10_by_type <- tfidf_by_type %>%
  group_by(participant_type) %>%
  slice_max(tf_idf, n = 10, with_ties = FALSE) %>%
  ungroup()

tfidf_top10_by_type
```

```{r}
word_compare <- tokens_clean %>%
  count(participant_type, word) %>%
  filter(participant_type %in% c("student", "supervisor")) %>%
  pivot_wider(names_from = participant_type, values_from = n, values_fill = 0)

ggplot(word_compare, aes(x = student + 1, y = supervisor + 1)) +
  geom_point(alpha = 0.5) +
  scale_x_log10() +
  scale_y_log10() +
  labs(
    title = "Word Frequency in Student vs Supervisor Texts",
    x = "Student Frequency (log scale)",
    y = "Supervisor Frequency (log scale)"
  )
```

```{r}
word_compare <- tokens_clean %>%
  count(participant_type, word) %>%
  filter(participant_type %in% c("student", "supervisor")) %>%
  pivot_wider(names_from = participant_type, values_from = n, values_fill = 0)

word_compare_plot <- ggplot(word_compare, aes(x = student + 1, y = supervisor + 1)) +
  geom_point(alpha = 0.5) +
  scale_x_log10() +
  scale_y_log10() +
  labs(
    title = "Word Frequency in Student vs Supervisor Texts",
    x = "Student Frequency (log scale)",
    y = "Supervisor Frequency (log scale)"
  )

word_compare_plot

ggsave(
  filename = "outputs/figures/word_frequency_student_vs_supervisor.png",
  plot = word_compare_plot,
  width = 8,
  height = 6,
  dpi = 300
)
```

```{r}
word_compare_plot <- ggplot(word_compare, aes(x = student + 1, y = supervisor + 1)) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_point(alpha = 0.5) +
  scale_x_log10() +
  scale_y_log10() +
  labs(
    title = "Word Frequency in Student vs Supervisor Texts",
    x = "Student Frequency (log scale)",
    y = "Supervisor Frequency (log scale)"
  )
```