---
title: "Final Project: HIP Analysis"
author: "Ariunjargal Khaltarkhuu"
date: today
format: pdf
editor: source
python:
  executable: "/opt/anaconda3/envs/textmining/bin/python"
---
# Install and Load Packages

```{r}
#install.packages(c(
  "tidyverse",
  "readtext",
  "tidytext",
  "quanteda",
  "quanteda.textstats",
  "quanteda.textplots",
  "topicmodels",
  "stm",
  "janitor",
  "stringr",
  "lubridate",
  "textstem",
  "widyr",
  "tidylo"
))
```

```{r}
library(tidyverse)
library(readtext)
library(tidytext)
library(quanteda)
library(quanteda.textstats)
library(quanteda.textplots)
library(topicmodels)
library(stm)
library(janitor)
library(stringr)
library(lubridate)
library(textstem)
library(widyr)
library(tidylo)
```

# Import and merge all text, metadata
```{r}
journals <- readtext("data_clean_archival/journals/*.txt")
interviews <- readtext("data_clean_archival/interviews/*.txt")
```

```{r}
all_text <- bind_rows(journals, interviews)
```

```{r}
all_text <- all_text %>%
  rename(file_name = doc_id,
         text_original = text)
```

```{r}
library(readr)
library(janitor)

meta <- read_csv("metadata/document_metadata.csv") %>%
  clean_names()
```

```{r}
summary(meta)
```

```{r}
glimpse(meta)
```

```{r}
table(meta$participant_type, useNA = "ifany")
table(meta$week_number, useNA = "ifany")
table(meta$work_mode, useNA = "ifany")
```

```{r}
library(dplyr)
library(stringr)
library(readr)

meta <- read_csv("metadata/document_metadata.csv")

meta <- meta %>%
  mutate(
    organization_name = str_trim(organization_name),
    organization_name = case_when(
      organization_name == "Engineers Without Border" ~ "Engineers Without Borders",
      organization_name == "Save The Children" ~ "Save the Children",
      organization_name == "GWU" ~ "George Washington University",
      TRUE ~ organization_name
    )
  )

sort(unique(meta$organization_name))

write_csv(meta, "metadata/document_metadata.csv")
```

```{r}
meta %>%
  count(organization_name, sort = TRUE)
```

```{r}
all_text <- bind_rows(journals, interviews) %>%
  rename(file_name = doc_id,
         text_original = text)

corpus_df <- all_text %>%
  left_join(meta, by = "file_name")
```

```{r}
glimpse(corpus_df)
sum(is.na(corpus_df$doc_id.y))
```

```{r}
library(dplyr)

all_text <- bind_rows(journals, interviews) %>%
  rename(
    file_name = doc_id,
    text_original = text
  )

corpus_df <- all_text %>%
  left_join(meta, by = "file_name")
```

```{r}
glimpse(corpus_df)

sum(is.na(corpus_df$doc_id.y))
sum(is.na(corpus_df$participant_type))
```

```{r}
names(corpus_df)
```

```{r}
corpus_df %>%
  filter(is.na(participant_type)) %>%
  select(file_name)
```

```{r}
all_text %>%
  anti_join(meta, by = "file_name") %>%
  select(file_name)
```

```{r}
meta %>%
  anti_join(all_text, by = "file_name") %>%
  select(file_name)
```

```{r}
corpus_df <- all_text %>%
  left_join(meta, by = "file_name")
```

```{r}
meta <- read_csv("metadata/document_metadata.csv") %>%
  clean_names()

meta <- meta %>%
  mutate(
    file_name = if_else(
      file_name == "supervisor_13_finalinterview.txt",
      "supervisor_13-finalinterview.txt",
      file_name
    )
  )

all_text <- bind_rows(journals, interviews) %>%
  rename(
    file_name = doc_id,
    text_original = text
  )

corpus_df <- all_text %>%
  left_join(meta, by = "file_name")

sum(is.na(corpus_df$participant_type))
```

# Create method specific corpus
```{r}
library(stringr)
library(dplyr)

corpus_df <- corpus_df %>%
  as_tibble() %>%
  mutate(
    text_ner = str_squish(text_original),

    text_tf = text_original %>%
      str_replace_all("\\[.*?\\]", " ") %>%
      str_to_lower() %>%
      str_replace_all("[^[:alnum:]\\s]", " ") %>%
      str_squish(),

    text_lda = text_original %>%
      str_replace_all("\\[.*?\\]", " ") %>%
      str_to_lower() %>%
      str_replace_all("[^[:alnum:]\\s]", " ") %>%
      str_squish()
  )
```
```{r}
names(corpus_df)
```

```{r}
corpus_df <- corpus_df %>%
  mutate(word_count = str_count(text_original, "\\S+"))

corpus_df %>% count(participant_type)
corpus_df %>% count(early_late)
summary(corpus_df$word_count)
```

# Tokenization for TF/TF-IDF/N-grams
```{r}
data(stop_words)

tokens <- corpus_df %>%
  select(doc_id, participant_type, early_late, cohort_year, organization_name, work_mode, text_tf) %>%
  unnest_tokens(word, text_tf)

tokens_clean <- tokens %>%
  anti_join(stop_words, by = "word")
```

```{r}
tokens_clean %>% count(word, sort = TRUE)
```

## Inductive- TF stage
```{r}
library(tidyverse)
library(tidytext)
library(stringr)
library(forcats)
```

```{r}
names(corpus_df)
```
```{r}
data(stop_words)

tokens <- corpus_df %>%
  select(
    doc_id,
    participant_type,
    participant_id,
    week_number,
    timepoint,
    early_late,
    cohort_year,
    organization_name,
    work_mode,
    text_tf
  ) %>%
  unnest_tokens(word, text_tf)
```
```{r}
glimpse(tokens)
```
```{r}
tokens_nostop <- tokens %>%
  anti_join(stop_words, by = "word")
```

```{r}
generic_project_words <- tibble(
  word = c(
    "intern", "interns", "internship", "student", "students", "bit",
    "project", "projects", "work", "working", "worked", "guys",
    "organization", "team", "program", "week", "weeks", "yeah",
    "really", "also", "would", "could", "one", "like", "just", "lot", "don", "day", "didn", "ve"
  )
)

tokens_clean <- tokens_nostop %>%
  anti_join(generic_project_words, by = "word")
```

```{r}
tokens_clean %>%
  count(word, sort = TRUE)
```

# Top words in student journals
```{r}
tf_students <- tokens_clean %>%
  filter(participant_type == "student") %>%
  count(word, sort = TRUE)

tf_students %>% slice_head(n = 25)
```

# Top words in supervisor interviews
```{r}
tf_supervisors <- tokens_clean %>%
  filter(participant_type == "supervisor") %>%
  count(word, sort = TRUE)

tf_supervisors %>% slice_head(n = 25)
```

# Visualize top words by participant type
```{r}
tf_top10_plot <- tf_by_type %>%
  group_by(participant_type) %>%
  slice_max(n, n = 10, with_ties = FALSE) %>%
  ungroup() %>%
  mutate(word = tidytext::reorder_within(word, n, participant_type)) %>%
  ggplot(aes(x = word, y = n)) +
  geom_col() +
  coord_flip() +
  tidytext::scale_x_reordered() +
  facet_wrap(~ participant_type, scales = "free_y") +
  labs(
    title = "Top 10 Words by Participant Type",
    x = NULL,
    y = "Term Frequency"
  )

tf_top10_plot
```

```{r}
ggsave(
  "outputs/figures/top10_words_by_participant_type.png",
  tf_top10_plot,
  width = 8,
  height = 6
)
```

# TF within positive, challenge, and skill-related contexts
```{r}
positive_seed <- c(
  "support", "helpful", "help", "great", "good", "positive",
  "confident", "confidence", "growth", "learning", "learned",
  "mentorship", "mentor", "professional", "success", "successful",
  "valuable", "meaningful", "prepared", "strong", "excited"
)
```

```{r}
challenge_seed <- c(
  "challenge", "challenges", "difficult", "difficulty", "hard",
  "unclear", "confusing", "stress", "stressed", "workload",
  "communication", "issue", "issues", "problem", "problems",
  "uncertainty", "logistics", "remote", "time", "busy"
)
```

```{r}
skill_seed <- c(
  "communication", "leadership", "analysis", "analytical",
  "research", "writing", "management", "teamwork", "collaboration",
  "problem", "technical", "data", "presentation", "organization"
)
```

# Create context-level subsets

```{r}
positive_docs <- tokens_clean %>%
  filter(word %in% positive_seed) %>%
  distinct(doc_id)

tokens_positive <- tokens_clean %>%
  semi_join(positive_docs, by = "doc_id")
```

```{r}
challenge_docs <- tokens_clean %>%
  filter(word %in% challenge_seed) %>%
  distinct(doc_id)

tokens_challenge <- tokens_clean %>%
  semi_join(challenge_docs, by = "doc_id")
```

```{r}
skill_docs <- tokens_clean %>%
  filter(word %in% skill_seed) %>%
  distinct(doc_id)

tokens_skill <- tokens_clean %>%
  semi_join(skill_docs, by = "doc_id")
```

# TF for positive/strength-related terms
```{r}
tf_positive_students <- tokens_positive %>%
  filter(participant_type == "student") %>%
  count(word, sort = TRUE)

tf_positive_students %>% slice_head(n = 20)
```

```{r}
tf_positive_supervisors <- tokens_positive %>%
  filter(participant_type == "supervisor") %>%
  count(word, sort = TRUE)

tf_positive_supervisors %>% slice_head(n = 20)
```

```{r}
bind_rows(
  tf_positive_students %>% mutate(group = "student"),
  tf_positive_supervisors %>% mutate(group = "supervisor")
) %>%
  group_by(group) %>%
  slice_max(n, n = 10) %>%
  ungroup() %>%
  mutate(word = reorder_within(word, n, group)) %>%
  ggplot(aes(x = word, y = n)) +
  geom_col() +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ group, scales = "free_y") +
  labs(
    title = "Top Words in Positive/Strength-Related Contexts",
    x = NULL,
    y = "Term Frequency"
  )
```

```{r}
positive_plot <- bind_rows(
  tf_positive_students %>% mutate(group = "student"),
  tf_positive_supervisors %>% mutate(group = "supervisor")
) %>%
  group_by(group) %>%
  slice_max(n, n = 10, with_ties = FALSE) %>%
  ungroup() %>%
  mutate(word = reorder_within(word, n, group)) %>%
  ggplot(aes(x = word, y = n)) +
  geom_col() +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ group, scales = "free_y") +
  labs(
    title = "Top Words in Positive/Strength-Related Contexts",
    x = NULL,
    y = "Term Frequency"
  )

ggsave(
  filename = "outputs/figures/top_words_positive_strength_contexts.png",
  plot = positive_plot,
  width = 8,
  height = 6,
  dpi = 300
)
```

# TF for challenge-related terms
```{r}
tf_challenge_by_type <- tokens_clean %>%
  filter(word %in% challenge_seed) %>%
  count(participant_type, word, sort = TRUE)

tf_challenge_top10 <- tf_challenge_by_type %>%
  group_by(participant_type) %>%
  slice_max(n, n = 10, with_ties = FALSE) %>%
  ungroup()

tf_challenge_top10
```

```{r}
challenge_plot <- tf_challenge_top10 %>%
  mutate(word = reorder_within(word, n, participant_type)) %>%
  ggplot(aes(x = word, y = n)) +
  geom_col() +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ participant_type, scales = "free_y") +
  labs(
    title = "Top 10 Challenge-Related Words by Participant Type",
    x = NULL,
    y = "Term Frequency"
  )

challenge_plot
```

```{r}
ggsave(
  filename = "outputs/figures/top10_challenge_words_by_participant_type.png",
  plot = challenge_plot,
  width = 8,
  height = 6,
  dpi = 300
)
```

```{r}
write_csv(
  tf_challenge_top10,
  "outputs/tables/top10_challenge_words_by_participant_type.csv"
)
```

# TF by subgroup- top words by early vs late among students
```{r}
tf_student_earlylate <- tokens_clean %>%
  filter(participant_type == "student") %>%
  count(early_late, word, sort = TRUE)

tf_student_earlylate %>%
  group_by(early_late) %>%
  slice_max(n, n = 15) %>%
  ungroup()
```

```{r}
tf_student_earlylate %>%
  group_by(early_late) %>%
  slice_max(n, n = 10) %>%
  ungroup() %>%
  mutate(word = reorder_within(word, n, early_late)) %>%
  ggplot(aes(x = word, y = n)) +
  geom_col() +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ early_late, scales = "free_y") +
  labs(
    title = "Top Words in Student Journals: Early vs Late",
    x = NULL,
    y = "Term Frequency"
  )
```

```{r}
tf_by_workmode <- tokens_clean %>%
  count(work_mode, word, sort = TRUE)

tf_by_workmode %>%
  group_by(work_mode) %>%
  slice_max(n, n = 15) %>%
  ungroup()
```

```{r}
tf_by_workmode <- tokens_clean %>%
  filter(!is.na(work_mode), work_mode != "NA") %>%
  count(work_mode, word, sort = TRUE)

workmode_plot <- tf_by_workmode %>%
  group_by(work_mode) %>%
  slice_max(n, n = 10, with_ties = FALSE) %>%
  ungroup() %>%
  mutate(word = reorder_within(word, n, work_mode)) %>%
  ggplot(aes(x = word, y = n)) +
  geom_col() +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ work_mode, scales = "free_y") +
  labs(
    title = "Top 10 Words by Work Mode",
    x = NULL,
    y = "Term Frequency"
  )

workmode_plot
```

```{r}
ggsave(
  filename = "outputs/figures/top10_words_by_work_mode.png",
  plot = workmode_plot,
  width = 8,
  height = 6,
  dpi = 300
)
```

## Inductive-TF-IDF stage

```{r}
library(tidyverse)
library(tidytext)
library(stringr)
library(forcats)

data(stop_words)

tokens <- corpus_df %>%
  select(
    doc_id,
    participant_type,
    participant_id,
    week_number,
    timepoint,
    early_late,
    cohort_year,
    organization_name,
    work_mode,
    text_tf
  ) %>%
  unnest_tokens(word, text_tf)

generic_project_words <- tibble(
  word = c(
    "intern", "interns", "internship", "internships", "set", "feel",
    "student", "students", "supervisor", "supervisors", "couple", "dhis2",
    "program", "programs", "project", "projects", "including", "wasn",
    "organization", "team", "work", "worked", "working", "00",
    "week", "weeks", "summer", "bit", "guys", "yeah", "so", "ll", "send",
    "gw", "hipp", "really", "also", "would", "could", "one", "like", "just", "lot", "don", "day", "didn", "ve", "pretty", "much", "thing", "things", "know", "got", "get", "getting", "people", "time", "times", "folks", "jasmine"
  )
)

tokens_clean <- tokens %>%
  anti_join(stop_words, by = "word") %>%
  anti_join(generic_project_words, by = "word")
```

# Compute by participant type

```{r}
tfidf_by_type <- tokens_clean %>%
  count(participant_type, word, sort = TRUE) %>%
  bind_tf_idf(word, participant_type, n) %>%
  arrange(desc(tf_idf))
```

```{r}
tfidf_top10_by_type <- tfidf_by_type %>%
  group_by(participant_type) %>%
  slice_max(tf_idf, n = 10, with_ties = FALSE) %>%
  ungroup()

tfidf_top10_by_type
```

```{r}
tfidf_type_plot <- tfidf_top10_by_type %>%
  mutate(word = reorder_within(word, tf_idf, participant_type)) %>%
  ggplot(aes(x = word, y = tf_idf)) +
  geom_col() +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ participant_type, scales = "free_y") +
  labs(
    title = "Top 10 Distinctive Words by Participant Type (TF-IDF)",
    x = NULL,
    y = "TF-IDF"
  )

tfidf_type_plot
```

```{r}
ggsave(
  filename = "outputs/figures/top10_tfidf_by_participant_type.png",
  plot = tfidf_type_plot,
  width = 8,
  height = 6,
  dpi = 300
)
```

```{r}
write_csv(
  tfidf_top10_by_type,
  "outputs/tables/top10_tfidf_by_participant_type.csv"
)
```

# Compute TF-IDF by early vs late journals

```{r}
tokens_students <- tokens_clean %>%
  filter(participant_type == "student")
```

```{r}
tfidf_earlylate <- tokens_students %>%
  count(early_late, word, sort = TRUE) %>%
  bind_tf_idf(word, early_late, n) %>%
  arrange(desc(tf_idf))
```

```{r}
tfidf_top10_earlylate <- tfidf_earlylate %>%
  group_by(early_late) %>%
  slice_max(tf_idf, n = 10, with_ties = FALSE) %>%
  ungroup()

tfidf_top10_earlylate
```

```{r}
tfidf_earlylate_plot <- tfidf_top10_earlylate %>%
  mutate(word = reorder_within(word, tf_idf, early_late)) %>%
  ggplot(aes(x = word, y = tf_idf)) +
  geom_col() +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ early_late, scales = "free_y") +
  labs(
    title = "Top 10 Distinctive Words in Early vs Late Student Reflections",
    x = NULL,
    y = "TF-IDF"
  )

tfidf_earlylate_plot
```

```{r}
ggsave(
  filename = "outputs/figures/top10_tfidf_early_vs_late.png",
  plot = tfidf_earlylate_plot,
  width = 8,
  height = 6,
  dpi = 300
)

write_csv(
  tfidf_top10_earlylate,
  "outputs/tables/top10_tfidf_early_vs_late.csv"
)
```

# Compute TF-IDF by work mode (wordcloud)
```{r}
# install.packages("ggwordcloud")
```

```{r}
library(ggwordcloud)
```

```{r}
tokens_workmode <- tokens_clean %>%
  filter(!is.na(work_mode), work_mode != "NA")

tfidf_workmode <- tokens_workmode %>%
  count(work_mode, word, sort = TRUE) %>%
  bind_tf_idf(word, work_mode, n) %>%
  arrange(desc(tf_idf))

tfidf_top10_workmode <- tfidf_workmode %>%
  group_by(work_mode) %>%
  slice_max(tf_idf, n = 20, with_ties = FALSE) %>%
  ungroup()

tfidf_top10_workmode
```

```{r}
tfidf_workmode_wordcloud <- tfidf_top10_workmode %>%
  ggplot(aes(label = word, size = tf_idf)) +
  geom_text_wordcloud_area() +
  facet_wrap(~ work_mode, scales = "free") +
  scale_size_area(max_size = 18) +
  labs(
    title = "Top 20 Distinctive Words by Work Mode (TF-IDF Word Cloud)"
  ) +
  theme_minimal()

tfidf_workmode_wordcloud
```

```{r}
ggsave(
  filename = "outputs/figures/top20_tfidf_wordcloud_by_work_mode.png",
  plot = tfidf_workmode_wordcloud,
  width = 10,
  height = 6,
  dpi = 300
)
```

```{r}
write_csv(
  tfidf_top10_workmode,
  "outputs/tables/top20_tfidf_by_work_mode.csv"
)
```

# RQ1: TF-IDF for strength-related terms
```{r}
positive_seed <- c(
  "support", "helpful", "help", "great", "good", "positive",
  "confident", "confidence", "growth", "learning", "learned",
  "mentorship", "mentor", "professional", "success", "successful",
  "valuable", "meaningful", "prepared", "strong", "excited"
)
```

```{r}
tfidf_strength_by_type <- tokens_clean %>%
  filter(word %in% positive_seed) %>%
  count(participant_type, word, sort = TRUE) %>%
  bind_tf_idf(word, participant_type, n) %>%
  arrange(desc(tf_idf))
```

```{r}
tfidf_strength_top10 <- tfidf_strength_by_type %>%
  group_by(participant_type) %>%
  slice_max(tf_idf, n = 10, with_ties = FALSE) %>%
  ungroup()

tfidf_strength_top10
```

```{r}
tfidf_strength_plot <- tfidf_strength_top10 %>%
  mutate(word = reorder_within(word, tf_idf, participant_type)) %>%
  ggplot(aes(x = word, y = tf_idf)) +
  geom_col() +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ participant_type, scales = "free_y") +
  labs(
    title = "Top 10 Distinctive Strength-Related Words by Participant Type",
    x = NULL,
    y = "TF-IDF"
  )

tfidf_strength_plot
```

```{r}
ggsave(
  filename = "outputs/figures/top10_tfidf_strength_by_participant_type.png",
  plot = tfidf_strength_plot,
  width = 8,
  height = 6,
  dpi = 300
)

write_csv(
  tfidf_strength_top10,
  "outputs/tables/top10_tfidf_strength_by_participant_type.csv"
)
```

```{r}
tfidf_strength_top10 %>%
  mutate(word = reorder_within(word, tf_idf, participant_type)) %>%
  ggplot(aes(x = word, y = tf_idf)) +
  geom_segment(aes(xend = word, y = 0, yend = tf_idf)) +
  geom_point(size = 3) +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ participant_type, scales = "free_y") +
  labs(
    title = "Distinctive Strength-Related Terms by Participant Type",
    x = NULL,
    y = "TF-IDF"
  )
```

```{r}
strength_lollipop_plot <- tfidf_strength_top10 %>%
  mutate(word = reorder_within(word, tf_idf, participant_type)) %>%
  ggplot(aes(x = word, y = tf_idf)) +
  geom_segment(aes(xend = word, y = 0, yend = tf_idf)) +
  geom_point(size = 3) +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ participant_type, scales = "free_y") +
  labs(
    title = "Distinctive Strength-Related Terms by Participant Type",
    x = NULL,
    y = "TF-IDF"
  )

strength_lollipop_plot

ggsave(
  filename = "outputs/figures/distinctive_strength_terms_lollipop.png",
  plot = strength_lollipop_plot,
  width = 8,
  height = 6,
  dpi = 300
)
```

```{r}
tfidf_strength_top10 %>%
  ggplot(aes(x = participant_type, y = word, fill = tf_idf)) +
  geom_tile() +
  labs(
    title = "Strength-Related TF-IDF by Participant Type",
    x = NULL,
    y = NULL,
    fill = "TF-IDF"
  )
```

```{r}
strength_heatmap <- tfidf_strength_top10 %>%
  ggplot(aes(x = participant_type, y = word, fill = tf_idf)) +
  geom_tile(color = "white") +
  labs(
    title = "Strength-Related TF-IDF by Participant Type",
    x = NULL,
    y = NULL,
    fill = "TF-IDF"
  )

strength_heatmap
```

```{r}
ggsave(
  filename = "outputs/figures/strength_tfidf_heatmap_by_participant_type.png",
  plot = strength_heatmap,
  width = 7,
  height = 6,
  dpi = 300
)
```

# RQ2: TF-IDF for challenge-related terms

```{r}
challenge_seed <- c(
  "challenge", "challenges", "difficult", "difficulty", "hard",
  "unclear", "confusing", "stress", "stressed", "workload",
  "communication", "issue", "issues", "problem", "problems",
  "uncertainty", "logistics", "remote", "time", "busy"
)
```

```{r}
tfidf_challenge_by_type <- tokens_clean %>%
  filter(word %in% challenge_seed) %>%
  count(participant_type, word, sort = TRUE) %>%
  bind_tf_idf(word, participant_type, n) %>%
  arrange(desc(tf_idf))
```

```{r}
tfidf_challenge_top10 <- tfidf_challenge_by_type %>%
  group_by(participant_type) %>%
  slice_max(tf_idf, n = 10, with_ties = FALSE) %>%
  ungroup()

tfidf_challenge_top10
```

```{r}
tfidf_challenge_plot <- tfidf_challenge_top10 %>%
  mutate(word = reorder_within(word, tf_idf, participant_type)) %>%
  ggplot(aes(x = word, y = tf_idf)) +
  geom_col() +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ participant_type, scales = "free_y") +
  labs(
    title = "Top 10 Distinctive Challenge-Related Words by Participant Type",
    x = NULL,
    y = "TF-IDF"
  )

tfidf_challenge_plot
```

```{r}
ggsave(
  filename = "outputs/figures/top10_tfidf_challenge_by_participant_type.png",
  plot = tfidf_challenge_plot,
  width = 8,
  height = 6,
  dpi = 300
)

write_csv(
  tfidf_challenge_top10,
  "outputs/tables/top10_tfidf_challenge_by_participant_type.csv"
)
```

```{r}
challenge_compare <- tfidf_challenge_by_type %>%
  filter(word %in% c("uncertainty", "stress", "confusing", "hard", "busy", "remote")) %>%
  select(participant_type, word, tf_idf)

ggplot(challenge_compare, aes(x = tf_idf, y = word, color = participant_type)) +
  geom_point(size = 3, position = position_dodge(width = 0.5)) +
  labs(
    title = "Challenge Language by Participant Type",
    x = "TF-IDF",
    y = NULL
  )
```

```{r}
challenge_compare <- tfidf_challenge_by_type %>%
  filter(word %in% c("uncertainty", "stress", "confusing", "hard", "busy", "remote")) %>%
  select(participant_type, word, tf_idf)

challenge_compare_plot <- ggplot(
  challenge_compare,
  aes(x = tf_idf, y = word, color = participant_type)
) +
  geom_point(size = 3, position = position_dodge(width = 0.5)) +
  labs(
    title = "Challenge Language by Participant Type",
    x = "TF-IDF",
    y = NULL
  )

challenge_compare_plot

ggsave(
  filename = "outputs/figures/challenge_language_by_participant_type.png",
  plot = challenge_compare_plot,
  width = 8,
  height = 6,
  dpi = 300
)
```

# 10. RQ3: skill-related language
```{r}
skill_seed <- c(
  "project", "management", "data", "analysis", "communication",
  "skills", "teamwork", "critical", "thinking", "report", "writing",
  "leadership", "research", "presentation", "collaboration"
)
```

```{r}
tfidf_skill_students <- tokens_clean %>%
  filter(participant_type == "student", word %in% skill_seed) %>%
  count(early_late, word, sort = TRUE) %>%
  bind_tf_idf(word, early_late, n) %>%
  arrange(desc(tf_idf))
```

```{r}
tfidf_skill_top10 <- tfidf_skill_students %>%
  group_by(early_late) %>%
  slice_max(tf_idf, n = 10, with_ties = FALSE) %>%
  ungroup()

tfidf_skill_top10
```

```{r}
tfidf_skill_plot <- tfidf_skill_top10 %>%
  mutate(word = reorder_within(word, tf_idf, early_late)) %>%
  ggplot(aes(x = word, y = tf_idf)) +
  geom_col() +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ early_late, scales = "free_y") +
  labs(
    title = "Top 10 Distinctive Skill-Related Words in Early vs Late Student Journals",
    x = NULL,
    y = "TF-IDF"
  )

tfidf_skill_plot
```

```{r}
ggsave(
  filename = "outputs/figures/top10_tfidf_skill_early_vs_late.png",
  plot = tfidf_skill_plot,
  width = 8,
  height = 6,
  dpi = 300
)

write_csv(
  tfidf_skill_top10,
  "outputs/tables/top10_tfidf_skill_early_vs_late.csv"
)
```

# RQ4: TF-IDF by subgroup
```{r}
tfidf_by_org <- tokens_clean %>%
  count(organization_name, word, sort = TRUE) %>%
  bind_tf_idf(word, organization_name, n) %>%
  arrange(desc(tf_idf))

tfidf_top10_by_org <- tfidf_by_org %>%
  group_by(organization_name) %>%
  slice_max(tf_idf, n = 10, with_ties = FALSE) %>%
  ungroup()
```

```{r}
tfidf_org_plot <- tfidf_top10_by_org %>%
  mutate(word = reorder_within(word, tf_idf, organization_name)) %>%
  ggplot(aes(x = word, y = tf_idf)) +
  geom_col() +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ organization_name, scales = "free_y") +
  labs(
    title = "Top 10 Distinctive Words by Organization",
    x = NULL,
    y = "TF-IDF"
  )

tfidf_org_plot
```

```{r}
ggsave(
  filename = "outputs/figures/top10_tfidf_by_organization.png",
  plot = tfidf_org_plot,
  width = 10,
  height = 8,
  dpi = 300
)

write_csv(
  tfidf_top10_by_org,
  "outputs/tables/top10_tfidf_by_organization.csv"
)
```

```{r}
tfidf_by_type <- tokens_clean %>%
  count(participant_type, word, sort = TRUE) %>%
  bind_tf_idf(word, participant_type, n) %>%
  arrange(desc(tf_idf))

tfidf_top10_by_type <- tfidf_by_type %>%
  group_by(participant_type) %>%
  slice_max(tf_idf, n = 10, with_ties = FALSE) %>%
  ungroup()

tfidf_top10_by_type
```

```{r}
word_compare <- tokens_clean %>%
  count(participant_type, word) %>%
  filter(participant_type %in% c("student", "supervisor")) %>%
  pivot_wider(names_from = participant_type, values_from = n, values_fill = 0)

ggplot(word_compare, aes(x = student + 1, y = supervisor + 1)) +
  geom_point(alpha = 0.5) +
  scale_x_log10() +
  scale_y_log10() +
  labs(
    title = "Word Frequency in Student vs Supervisor Texts",
    x = "Student Frequency (log scale)",
    y = "Supervisor Frequency (log scale)"
  )
```

```{r}
word_compare <- tokens_clean %>%
  count(participant_type, word) %>%
  filter(participant_type %in% c("student", "supervisor")) %>%
  pivot_wider(names_from = participant_type, values_from = n, values_fill = 0)

word_compare_plot <- ggplot(word_compare, aes(x = student + 1, y = supervisor + 1)) +
  geom_point(alpha = 0.5) +
  scale_x_log10() +
  scale_y_log10() +
  labs(
    title = "Word Frequency in Student vs Supervisor Texts",
    x = "Student Frequency (log scale)",
    y = "Supervisor Frequency (log scale)"
  )

word_compare_plot

ggsave(
  filename = "outputs/figures/word_frequency_student_vs_supervisor.png",
  plot = word_compare_plot,
  width = 8,
  height = 6,
  dpi = 300
)
```

```{r}
word_compare_plot <- ggplot(word_compare, aes(x = student + 1, y = supervisor + 1)) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_point(alpha = 0.5) +
  scale_x_log10() +
  scale_y_log10() +
  labs(
    title = "Word Frequency in Student vs Supervisor Texts",
    x = "Student Frequency (log scale)",
    y = "Supervisor Frequency (log scale)"
  )
```

## Inductive- N-grams stage

```{r}
meta <- read_csv("metadata/document_metadata.csv") %>%
  clean_names()
```

```{r}
all_text <- bind_rows(journals, interviews) %>%
  rename(
    file_name = doc_id,
    text_original = text
  ) %>%
  as_tibble()
```

```{r}
corpus_df <- all_text %>%
  left_join(meta, by = "file_name") %>%
  as_tibble()
```

```{r}
glimpse(corpus_df)
sum(is.na(corpus_df$participant_type))
```

```{r}
corpus_df <- corpus_df %>%
  mutate(
    text_ner = str_squish(text_original),
    text_tf = text_original %>%
      str_replace_all("\\[.*?\\]", " ") %>%
      str_to_lower() %>%
      str_replace_all("[^[:alnum:]\\s]", " ") %>%
      str_squish(),
    text_lda = text_original %>%
      str_replace_all("\\[.*?\\]", " ") %>%
      str_to_lower() %>%
      str_replace_all("[^[:alnum:]\\s]", " ") %>%
      str_squish()
  )
```

```{r}
data(stop_words)

tokens <- corpus_df %>%
  select(
    doc_id,
    participant_type,
    participant_id,
    week_number,
    timepoint,
    early_late,
    cohort_year,
    organization_name,
    work_mode,
    text_tf
  ) %>%
  unnest_tokens(word, text_tf)

generic_project_words <- tibble(
  word = c(
    "intern", "interns", "internship", "internships",
    "student", "students", "supervisor", "supervisors",
    "program", "programs", "project", "projects",
    "organization", "team", "work", "worked", "working",
    "week", "weeks", "summer", "bit", "guys", "yeah", "so",
    "gw", "hipp", "really", "also", "would", "could", "one", "like", "just", "lot", "don", "day", "didn", "ve"
  )
)

tokens_clean <- tokens %>%
  anti_join(stop_words, by = "word") %>%
  anti_join(generic_project_words, by = "word")
```

```{r}
# Create bigrams
library(tidyverse)
library(tidytext)
library(stringr)
library(forcats)

bigrams <- corpus_df %>%
  select(
    doc_id,
    participant_type,
    early_late,
    work_mode,
    cohort_year,
    organization_name,
    text_tf
  ) %>%
  unnest_tokens(bigram, text_tf, token = "ngrams", n = 2)
```

```{r}
# Create trigrams
trigrams <- corpus_df %>%
  select(
    doc_id,
    participant_type,
    early_late,
    work_mode,
    cohort_year,
    organization_name,
    text_tf
  ) %>%
  unnest_tokens(trigram, text_tf, token = "ngrams", n = 3)
```

```{r}
# Clean bigrams
library(tidyverse)
library(tidytext)
library(stringr)

data(stop_words)

custom_filler_words <- tibble(
  word = c(
    "i", "im", "ive", "id",
    "think", "also", "just", "really", "kind", "sort",
    "like", "okay", "yeah", "yes", "no", "well"
  )
)

bigrams_clean_strict <- bigrams %>%
  separate(bigram, into = c("word1", "word2"), sep = " ") %>%
  filter(!is.na(word1), !is.na(word2)) %>%
  anti_join(stop_words, by = c("word1" = "word")) %>%
  anti_join(stop_words, by = c("word2" = "word")) %>%
  anti_join(custom_filler_words, by = c("word1" = "word")) %>%
  anti_join(custom_filler_words, by = c("word2" = "word")) %>%
  unite(bigram, word1, word2, sep = " ")
```

```{r}
# Clean trigrams
custom_filler_words <- tibble(
  word = c(
    "i", "im", "ive", "id",
    "think", "also", "just", "really", "kind", "sort",
    "like", "okay", "yeah", "yes", "no", "well"
  )
)

trigrams_clean_strict <- trigrams %>%
  separate(trigram, into = c("word1", "word2", "word3"), sep = " ") %>%
  filter(!is.na(word1), !is.na(word2), !is.na(word3)) %>%
  anti_join(stop_words, by = c("word1" = "word")) %>%
  anti_join(stop_words, by = c("word2" = "word")) %>%
  anti_join(stop_words, by = c("word3" = "word")) %>%
  anti_join(custom_filler_words, by = c("word1" = "word")) %>%
  anti_join(custom_filler_words, by = c("word2" = "word")) %>%
  anti_join(custom_filler_words, by = c("word3" = "word")) %>%
  unite(trigram, word1, word2, word3, sep = " ")
```

```{r}
# Inspect top bigrams
bigram_counts <- bigrams_clean %>%
  count(bigram, sort = TRUE)

bigram_counts %>% slice_head(n = 40)
```

```{r}
trigram_counts <- trigrams_clean %>%
  count(trigram, sort = TRUE)

trigram_counts %>% slice_head(n = 40)
```

```{r}
# example generic phrases
generic_bigrams <- tibble(
  bigram = c(
    "project hope",
    "world central",
    "central kitchen",
    "save the",
    "relief international",
    "the student",
    "this internship",
    "of the",
    "for the",
    "it was",
    "i think",
    "i was",
    "we had"
  )
)

generic_trigrams <- tibble(
  trigram = c(
    "world central kitchen",
    "one of the",
    "a lot of",
    "it was really",
    "this was really"
  )
)
```

```{r}
# Remove generic phrases
bigrams_clean2 <- bigrams_clean %>%
  anti_join(generic_bigrams, by = "bigram")

trigrams_clean2 <- trigrams_clean %>%
  anti_join(generic_trigrams, by = "trigram")
```

```{r}
bigrams_clean2 %>%
  count(bigram, sort = TRUE) %>%
  slice_head(n = 40)

trigrams_clean2 %>%
  count(trigram, sort = TRUE) %>%
  slice_head(n = 40)
```

```{r}
# remove more phrases from bigrams
junk_bigrams <- tibble(
  bigram = c(
    "she was", "with the", "plan to", "i plan", "the organization",
    "that she", "a lot", "in the", "don t", "to the", "it s",
    "that we", "and then", "have a", "that s", "on the", "lot of",
    "to be", "that was", "we have", "didn t", "i don", "a key",
    "and the", "able to", "was a", "how to", "in a", "and we", "to do"
  )
)
```

```{r}
# remove more phrases from trigrams
junk_trigrams <- tibble(
  trigram = c(
    "don t know", "the organization s", "a couple of", "t know if",
    "we have a", "with the student", "to complete the", "a little bit",
    "that she was", "the student was", "didn t have", "for the first",
    "for the organization", "if it s", "some of the", "to work with"
  )
)
```

```{r}
# apply
bigrams_clean3 <- bigrams_clean2 %>%
  anti_join(junk_bigrams, by = "bigram")

trigrams_clean3 <- trigrams_clean2 %>%
  anti_join(junk_trigrams, by = "trigram")
```

```{r}
# inspect again
bigrams_clean3 %>%
  count(bigram, sort = TRUE) %>%
  slice_head(n = 40)

trigrams_clean3 %>%
  count(trigram, sort = TRUE) %>%
  slice_head(n = 40)
```

```{r}
# final "junk phrase" removal bigrams
junk_bigrams2 <- tibble(
  bigram = c(
    "of our", "so that", "we were", "with my", "ability to",
    "aim to", "to have", "focused on", "from the", "so we",
    "the team", "a great", "an intern", "developed a"
  )
)
```

```{r}
# final "junk phrase" removal trigrams
junk_trigrams2 <- tibble(
  trigram = c(
    "plan to continue", "plan to complete", "plan to finalize",
    "was able to", "in terms of", "in the future",
    "the first week"
  )
)
```

```{r}
#apply
bigrams_clean4 <- bigrams_clean3 %>%
  anti_join(junk_bigrams2, by = "bigram")

trigrams_clean4 <- trigrams_clean3 %>%
  anti_join(junk_trigrams2, by = "trigram")
```

```{r}
bigrams_clean4 %>%
  count(bigram, sort = TRUE) %>%
  slice_head(n = 25)

trigrams_clean4 %>%
  count(trigram, sort = TRUE) %>%
  slice_head(n = 25)
```

```{r}
#final cleanup bigrams and trigrams
junk_bigrams3 <- tibble(
  bigram = c(
    "challenge i", "t know", "for a", "she s", "t have", "within the"
  )
)

junk_trigrams3 <- tibble(
  trigram = c(
    "the importance of", "mental health and", "don t have",
    "to finalize the", "be able to", "have a lot",
    "it s a", "it was a"
  )
)

bigrams_clean5 <- bigrams_clean4 %>%
  anti_join(junk_bigrams3, by = "bigram")

trigrams_clean5 <- trigrams_clean4 %>%
  anti_join(junk_trigrams3, by = "trigram")
```

```{r}
bigrams_clean5 %>%
  count(bigram, sort = TRUE) %>%
  slice_head(n = 25)

trigrams_clean5 %>%
  count(trigram, sort = TRUE) %>%
  slice_head(n = 25)
```

```{r}
# Strength phrase table
strength_patterns <- c(
  "strengthened my",
  "understanding of",
  "i gained",
  "my supervisor",
  "my ability to",
  "my understanding of",
  "strengthened my ability",
  "gained insight into",
  "to better understand",
  "a great job"
)

strength_phrases <- bind_rows(
  bigrams_clean5 %>%
    count(bigram, sort = TRUE) %>%
    filter(str_detect(bigram, str_c(strength_patterns, collapse = "|"))) %>%
    rename(phrase = bigram),
  trigrams_clean5 %>%
    count(trigram, sort = TRUE) %>%
    filter(str_detect(trigram, str_c(strength_patterns, collapse = "|"))) %>%
    rename(phrase = trigram)
) %>%
  arrange(desc(n))

strength_phrases
```

```{r}
# Challenge phrase table
challenge_patterns_refined <- c(
  "^a challenge involved$",
  "^a key challenge$",
  "^key challenge involved$",
  "^i encountered$",
  "^to address this$",
  "^addressed this by$",
  "^a challenge arose$"
)
```

```{r}
challenge_phrases_refined <- bind_rows(
  bigrams_clean5 %>%
    count(bigram, sort = TRUE) %>%
    rename(phrase = bigram),
  trigrams_clean5 %>%
    count(trigram, sort = TRUE) %>%
    rename(phrase = trigram)
) %>%
  filter(str_detect(phrase, str_c(challenge_patterns_refined, collapse = "|"))) %>%
  arrange(desc(n))

challenge_phrases_refined
```

```{r}
# skill phrase table
skill_patterns <- c(
  "monitoring and evaluation",
  "a key skill",
  "my ability to",
  "my understanding of",
  "strengthened my ability",
  "gained insight into",
  "my responsibilities included",
  "safety and security",
  "youth mental health"
)

skill_phrases <- bind_rows(
  bigrams_clean5 %>%
    count(bigram, sort = TRUE) %>%
    filter(str_detect(bigram, str_c(skill_patterns, collapse = "|"))) %>%
    rename(phrase = bigram),
  trigrams_clean5 %>%
    count(trigram, sort = TRUE) %>%
    filter(str_detect(trigram, str_c(skill_patterns, collapse = "|"))) %>%
    rename(phrase = trigram)
) %>%
  arrange(desc(n))

skill_phrases
```

```{r}
# strength lollipop chart
strength_phrase_plot <- strength_phrases %>%
  slice_max(n, n = 10, with_ties = FALSE) %>%
  mutate(phrase = fct_reorder(phrase, n)) %>%
  ggplot(aes(x = phrase, y = n)) +
  geom_segment(aes(xend = phrase, y = 0, yend = n)) +
  geom_point(size = 3) +
  coord_flip() +
  labs(
    title = "Top Strength-Related Phrases",
    x = NULL,
    y = "Frequency"
  )

strength_phrase_plot
```

```{r}
# save the strength lollipop chart
ggsave(
  filename = "outputs/figures/top_strength_phrases.png",
  plot = strength_phrase_plot,
  width = 8,
  height = 6,
  dpi = 300
)
```

```{r}
# save the challenge phrase table
write_csv(
  challenge_phrases_refined,
  "outputs/tables/challenge_phrases_refined.csv"
)
```

```{r}
# skill lollipoop chart
skill_phrase_plot <- skill_phrases %>%
  slice_max(n, n = 10, with_ties = FALSE) %>%
  mutate(phrase = fct_reorder(phrase, n)) %>%
  ggplot(aes(x = phrase, y = n)) +
  geom_segment(aes(xend = phrase, y = 0, yend = n)) +
  geom_point(size = 3) +
  coord_flip() +
  labs(
    title = "Top Skill-Related Phrases",
    x = NULL,
    y = "Frequency"
  )

skill_phrase_plot
```

```{r}
# save the skill lollipop chart
ggsave(
  filename = "outputs/figures/top_skill_phrases.png",
  plot = skill_phrase_plot,
  width = 8,
  height = 6,
  dpi = 300
)
```

```{r}
write_csv(strength_phrases, "outputs/tables/strength_phrases.csv")
write_csv(challenge_phrases, "outputs/tables/challenge_phrases.csv")
write_csv(skill_phrases, "outputs/tables/skill_phrases.csv")
```

# subgroup n-grams for RQ4

```{r}
# Early vs late bigrams
bigram_earlylate <- bigrams_clean5 %>%
  filter(participant_type == "student") %>%
  count(early_late, bigram, sort = TRUE)

bigram_earlylate_top10 <- bigram_earlylate %>%
  filter(!bigram %in% c("organization s", "the first", "to a", "we re", "at the")) %>%
  group_by(early_late) %>%
  slice_max(n, n = 10, with_ties = FALSE) %>%
  ungroup()

bigram_earlylate_top10
```

```{r}
# visualize early vs late bigrams (barchart)
bigram_earlylate_plot <- bigram_earlylate_top10 %>%
  mutate(bigram = reorder_within(bigram, n, early_late)) %>%
  ggplot(aes(x = bigram, y = n)) +
  geom_col() +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ early_late, scales = "free_y") +
  labs(
    title = "Top Phrases in Early vs Late Student Journals",
    x = NULL,
    y = "Frequency"
  )

bigram_earlylate_plot
```

```{r}
# save
ggsave(
  filename = "outputs/figures/top_phrases_early_vs_late.png",
  plot = bigram_earlylate_plot,
  width = 9,
  height = 6,
  dpi = 300
)
```

```{r}
# Hybrid vs remote bigrams
bigram_workmode <- bigrams_clean5 %>%
  filter(!is.na(work_mode), work_mode %in% c("hybrid", "remote")) %>%
  count(work_mode, bigram, sort = TRUE)

bigram_workmode_top10 <- bigram_workmode %>%
  filter(!bigram %in% c("organization s", "the first", "to a", "we re", "at the")) %>%
  group_by(work_mode) %>%
  slice_max(n, n = 10, with_ties = FALSE) %>%
  ungroup()

bigram_workmode_top10
```

```{r}
# Visualize hybrid vs remote bigrams
bigram_workmode_plot <- bigram_workmode_top10 %>%
  mutate(bigram = reorder_within(bigram, n, work_mode)) %>%
  ggplot(aes(x = bigram, y = n)) +
  geom_col() +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ work_mode, scales = "free_y") +
  labs(
    title = "Top Phrases by Work Mode",
    x = NULL,
    y = "Frequency"
  )

bigram_workmode_plot
```

```{r}
ggsave(
  filename = "outputs/figures/top_phrases_by_work_mode.png",
  plot = bigram_workmode_plot,
  width = 9,
  height = 6,
  dpi = 300
)
```

```{r}
strength_phrases
challenge_phrases
skill_phrases
```

## Inductive- NER stage (Python)

```{r}
library(reticulate)

use_python("/opt/anaconda3/envs/textmining/bin/python", required = TRUE)
py_config()
```

```{r}
py_install(c("spacy", "pandas", "matplotlib"), pip = TRUE)
```

```{r}
py <- py_config()$python
system2(py, c("-m", "spacy", "download", "en_core_web_sm"))
```

```{r}
spacy <- import("spacy")
nlp <- spacy$load("en_core_web_sm")
print("spaCy model loaded successfully")
```

```{r}
ner_input <- corpus_df %>%
  select(
    doc_id,
    participant_type,
    participant_id,
    early_late,
    work_mode,
    cohort_year,
    organization_name,
    text_ner
  )

write_csv(ner_input, "outputs/ner_input.csv")
```

```{r}
file.exists("outputs/ner_input.csv")
```

```{python}
import pandas as pd
import spacy
import re

nlp = spacy.load("en_core_web_sm")

df = pd.read_csv("outputs/ner_input.csv")
df.head()
```

```{python}
# Define evaluative context vocabularies
positive_words = {
    "support", "supportive", "help", "helpful", "great", "good", "excellent",
    "strong", "valuable", "meaningful", "prepared", "professional",
    "confident", "confidence", "growth", "learned", "learning",
    "successful", "success", "amazing", "positive",
    "gained", "strengthened", "insight", "understanding", "developed",
    "improved", "better", "clearer", "deeper", "responsive",
    "available", "encouraged", "encouraging"
}

challenge_words = {
    "challenge", "challenging", "difficult", "difficulty", "hard",
    "unclear", "confusing", "issue", "issues", "problem", "problems",
    "stress", "stressed", "workload", "pressure", "busy", "remote",
    "barrier", "barriers", "uncertainty", "limited",
    "encountered", "delay", "delays", "restructure", "restructuring",
    "cut", "cuts", "changed", "change", "demanding", "constraint",
    "constraints", "overwhelming", "lack"
}

support_actor_words = {
    "support", "help", "helpful", "guidance", "mentor", "mentorship",
    "encourage", "encouraged", "encouraging", "available", "responsive",
    "clear", "feedback", "check", "check-in", "checkins", "supervision",
    "welcoming", "professional", "prepared", "collaborative"
}

barrier_actor_words = {
    "unclear", "delay", "delays", "limited", "busy", "pressure",
    "uncertainty", "restructure", "restructuring", "cut", "cuts", "remote",
    "challenging", "issue", "issues", "problem", "problems",
    "lack", "barrier", "barriers", "overwhelming", "changed", "absence"
}

skill_words = {
    "analysis", "analytical", "data", "research", "writing", "report",
    "reporting", "communication", "presentation", "management",
    "monitoring", "evaluation", "coordination", "organization",
    "organizational", "leadership", "teamwork", "collaboration",
    "critical", "thinking", "problem", "solving", "skills",
    "responsibilities", "developed", "strengthened", "ability"
}
```

```{python}
# Add rule-based institutional actor patterns
role_patterns = [
    r"\bsupervisor\b",
    r"\bmanager\b",
    r"\bdirector\b",
    r"\bcoordinator\b",
    r"\bteam lead\b",
    r"\bleadership\b",
    r"\bstaff\b",
    r"\bdonor\b",
    r"\bcolleague\b",
    r"\bexecutive\b",
    r"\bboard\b",
    r"\bmentor\b",
    r"\bhr\b",
    r"\bceo\b"
]
```

```{python}
#Extract entities and nearby evaluative context
rows = []

for _, row in df.iterrows():
    doc_id = row["doc_id"]
    participant_type = row["participant_type"]
    early_late = row["early_late"]
    work_mode = row["work_mode"]
    cohort_year = row["cohort_year"]
    text = str(row["text_ner"])

    doc = nlp(text)

    # spaCy entities
    for ent in doc.ents:
        if ent.label_ in {"ORG", "GPE", "LOC", "PERSON"}:
            start = max(ent.start - 5, 0)
            end = min(ent.end + 5, len(doc))
            window_tokens = [t.text.lower() for t in doc[start:end]]
            window_text = " ".join(window_tokens)

            pos_flag = any(w in window_tokens for w in positive_words)
            chal_flag = any(w in window_tokens for w in challenge_words)
            support_flag = any(w in window_tokens for w in support_actor_words)
            barrier_flag = any(w in window_tokens for w in barrier_actor_words)

            rows.append({
                "doc_id": doc_id,
                "participant_type": participant_type,
                "early_late": early_late,
                "work_mode": work_mode,
                "cohort_year": cohort_year,
                "entity": ent.text,
                "entity_label": ent.label_,
                "window_text": window_text,
                "positive_context": int(pos_flag),
                "challenge_context": int(chal_flag),
                "support_context": int(support_flag),
                "barrier_context": int(barrier_flag)
            })

    # rule-based institutional actors
    lowered = text.lower()
    for pattern in role_patterns:
        for match in re.finditer(pattern, lowered):
            role = match.group(0)
            window_start = max(match.start() - 40, 0)
            window_end = min(match.end() + 40, len(lowered))
            window_text = lowered[window_start:window_end]

            pos_flag = any(w in window_text for w in positive_words)
            chal_flag = any(w in window_text for w in challenge_words)
            support_flag = any(w in window_text for w in support_actor_words)
            barrier_flag = any(w in window_text for w in barrier_actor_words)

            rows.append({
                "doc_id": doc_id,
                "participant_type": participant_type,
                "early_late": early_late,
                "work_mode": work_mode,
                "cohort_year": cohort_year,
                "entity": role,
                "entity_label": "ROLE",
                "window_text": window_text,
                "positive_context": int(pos_flag),
                "challenge_context": int(chal_flag),
                "support_context": int(support_flag),
                "barrier_context": int(barrier_flag)
            })

entities = pd.DataFrame(rows)
entities.head()
```

```{python}
entities["entity"] = (
    entities["entity"]
    .str.strip()
    .str.replace(r"\s+", " ", regex=True)
)

# Optional: standardize some variants
entities["entity"] = entities["entity"].replace({
    "gw": "GWU",
    "gwu": "GWU",
    "world central kitchen": "World Central Kitchen",
    "project hope": "Project Hope",
    "save the children": "Save the Children",
    "relief international": "Relief International",
    "care": "CARE"
})
```

```{python}
entities.to_csv("outputs/ner_entities_full.csv", index=False)
```

# Create summary tables 
```{python}
# Top organizations by participant type
org_by_type = (
    entities[entities["entity_label"] == "ORG"]
    .groupby(["participant_type", "entity"])
    .size()
    .reset_index(name="n")
    .sort_values(["participant_type", "n"], ascending=[True, False])
)

org_by_type.to_csv("outputs/ner_org_by_participant_type.csv", index=False)
org_by_type.head(20)
```

```{python}
# Top places by subgroup
place_by_subgroup = (
    entities[entities["entity_label"].isin(["GPE", "LOC"])]
    .groupby(["work_mode", "entity"])
    .size()
    .reset_index(name="n")
    .sort_values(["work_mode", "n"], ascending=[True, False])
)

place_by_subgroup.to_csv("outputs/ner_places_by_work_mode.csv", index=False)
place_by_subgroup.head(20)
```

```{python}
# Institutional actors with support/barrier context
roles_context = (
    entities[entities["entity_label"] == "ROLE"]
    .groupby("entity")[["support_context", "barrier_context", "positive_context", "challenge_context"]]
    .sum()
    .reset_index()
    .sort_values("support_context", ascending=False)
)

roles_context.to_csv("outputs/ner_roles_context.csv", index=False)
roles_context.head(20)
```

```{python}
# For RQ1 specific output
# Organizations mentioned in positive contexts
org_positive = (
    entities[(entities["entity_label"] == "ORG") & (entities["positive_context"] == 1)]
    .groupby("entity")
    .size()
    .reset_index(name="n")
    .sort_values("n", ascending=False)
)

org_positive.to_csv("outputs/ner_org_positive_context.csv", index=False)
org_positive.head(20)
```

```{python}
# For RQ1 specific output
# Institutional actors in positive/support contexts
role_positive = (
    entities[(entities["entity_label"] == "ROLE") & ((entities["positive_context"] == 1) | (entities["support_context"] == 1))]
    .groupby("entity")
    .size()
    .reset_index(name="n")
    .sort_values("n", ascending=False)
)

role_positive.to_csv("outputs/ner_roles_positive_context.csv", index=False)
role_positive.head(20)
```

```{python}
# For RQ4 specific output
# Organizations by work mode
org_by_workmode = (
    entities[entities["entity_label"] == "ORG"]
    .groupby(["work_mode", "entity"])
    .size()
    .reset_index(name="n")
    .sort_values(["work_mode", "n"], ascending=[True, False])
)

org_by_workmode.to_csv("outputs/ner_org_by_work_mode.csv", index=False)
```

```{python}
# For RQ4 specific output
# Locations by early/late
place_by_earlylate = (
    entities[entities["entity_label"].isin(["GPE", "LOC"])]
    .groupby(["early_late", "entity"])
    .size()
    .reset_index(name="n")
    .sort_values(["early_late", "n"], ascending=[True, False])
)

place_by_earlylate.to_csv("outputs/ner_places_by_earlylate.csv", index=False)
```

```{python}
# For RQ4 specific output
# Roles by subgroup
roles_by_type = (
    entities[entities["entity_label"] == "ROLE"]
    .groupby(["participant_type", "entity"])
    .size()
    .reset_index(name="n")
    .sort_values(["participant_type", "n"], ascending=[True, False])
)

roles_by_type.to_csv("outputs/ner_roles_by_participant_type.csv", index=False)
```

# Visualization code in Python

```{python}
import os
import matplotlib.pyplot as plt
```
```{python}
# Top organizations by participant type

top_org_by_type = (
    org_by_type
    .sort_values(["participant_type", "n"], ascending=[True, False])
    .groupby("participant_type")
    .head(10)
    .copy()
)

for group in top_org_by_type["participant_type"].dropna().unique():
    subset = (
        top_org_by_type[top_org_by_type["participant_type"] == group]
        .sort_values("n")
    )

    plt.figure(figsize=(8, 5))
    plt.barh(subset["entity"], subset["n"])
    plt.title(f"Top Organizations Mentioned: {group}")
    plt.xlabel("Count")
    plt.ylabel("")
    plt.tight_layout()
    plt.savefig(f"outputs/figures/ner_top_org_{group}.png", dpi=300, bbox_inches="tight")
    plt.close()
```

```{python}
# Top places by work mode

top_places_workmode = (
    place_by_subgroup
    .dropna(subset=["work_mode"])
    .sort_values(["work_mode", "n"], ascending=[True, False])
    .groupby("work_mode")
    .head(10)
    .copy()
)

for mode in top_places_workmode["work_mode"].unique():
    subset = (
        top_places_workmode[top_places_workmode["work_mode"] == mode]
        .sort_values("n")
    )

    safe_mode = str(mode).replace(" ", "_").replace("/", "_")

    plt.figure(figsize=(8, 5))
    plt.barh(subset["entity"], subset["n"])
    plt.title(f"Top Place Mentions: {mode}")
    plt.xlabel("Count")
    plt.ylabel("")
    plt.tight_layout()
    plt.savefig(f"outputs/figures/ner_top_places_{safe_mode}.png", dpi=300, bbox_inches="tight")
    plt.close()
```

```{python}
# Institutional actors: support vs barrier

top_roles = (
    roles_context
    .sort_values("support_context", ascending=False)
    .head(10)
    .copy()
    .sort_values("support_context")
)

plt.figure(figsize=(9, 6))
plt.barh(top_roles["entity"], top_roles["support_context"], label="Support")
plt.barh(
    top_roles["entity"],
    top_roles["barrier_context"],
    left=top_roles["support_context"],
    label="Barrier"
)
plt.title("Institutional Actors Associated with Support and Barriers")
plt.xlabel("Context Count")
plt.ylabel("")
plt.legend()
plt.tight_layout()
plt.savefig("outputs/figures/ner_roles_support_barrier.png", dpi=300, bbox_inches="tight")
plt.close()
```

# Optional heatmap
```{r}
roles_context <- read_csv("outputs/ner_roles_context.csv")
```

```{r}
roles_context_long <- roles_context %>%
  pivot_longer(
    cols = c(support_context, barrier_context, positive_context, challenge_context),
    names_to = "context_type",
    values_to = "count"
  )
```

```{r}
roles_context_heatmap <- roles_context_long %>%
  ggplot(aes(x = context_type, y = entity, fill = count)) +
  geom_tile(color = "white") +
  labs(
    title = "Institutional Actors by Evaluative Context",
    x = NULL,
    y = NULL,
    fill = "Count"
  )

roles_context_heatmap
```

```{r}
ggsave(
  filename = "outputs/figures/ner_roles_context_heatmap.png",
  plot = roles_context_heatmap,
  width = 8,
  height = 6,
  dpi = 300
)
```